The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-10 rational.tex
reorg

Multiplicative duality is added to {{langRev}} by adding types
{{1/b}}, values {{1/v}} and isomorphisms {{eta*}} and {{eps*}}.

@@

\noindent
These have the type judgments

%subcode{opsem} include main
% eta* &: 1 <-> (1/b) * b :& eps*

%subcode{proof} include main
%@ |- v : b
%@@ |- 1/v : 1/b

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Compact Closure with Multiplicative Inverses}

\paragraph*{Coherence.} 
As before, the requisite coherence condition on Compact Closed
Categories is applicable and is expressed below in terms of
{{eta*}}/{{eps*}} and the multiplicative monoid.

@@

@@

%%%%%%%%%%%%%%%%%%%%%
\subsection{Unification and Logic Programming}

@@

%%%%%%%%%%%%%%%%%%
\subsection{Constructions in {{langRevEE}} specific to Addition and Multiplication}
\label{sec:neg-constructions}

%% %%%%%%%%%%%%%%%%%%%%%%
%% \subsection{To think about}

%% \begin{itemize}

%% \item Can the operational semantics for {{langRevEE}} be an
%%   interpreter that is implemented in {{langRevT}} (similar to how the
%%   the tree traversal interpreter was implemented). This would imply
%%   the existence of a more powerful construction than Int, wherein the
%%   products would also be preserved. This is possibly worth a paper in
%%   itself.

%% \item 
%% \item

%% \begin{center}
%%   \includegraphics{diagrams/neg_circuit1.pdf}
%% \end{center}

%% \begin{center}
%%   \includegraphics{diagrams/neg_circuit2.pdf}
%% \end{center}

%% \end{itemize}

>>>>

Multiplicative duality is added to {{langRev}} by adding types
{{1/b}}, values {{1/v}} and isomorphisms {{eta*}} and {{eps*}} with
the following type judgements.

@@

\vspace{-15pt}
\begin{multicols}{2}
%subcode{opsem} include main
% eta* &: 1 <-> (1/b) * b :& eps*

%subcode{proof} include main
%@ |- v : b
%@@ |- 1/v : 1/b  
\end{multicols}

@@

\paragraph*{Coherence for Compact Closure with Multiplicative Inverses} 
As before, the requisite coherence condition on Compact Closed
Categories is applicable and is expressed below in terms of
{{eta*}}/{{eps*}} and the multiplicative monoid.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions in {{langRevEE}} specific to Addition and Multiplication}
\label{sec:neg-constructions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unification and Logic Programming}

@@
